---
title: "MLINDIV Structural Analysis A: Maze DVs"
author: "Alina Tu"
date: "`r Sys.Date()`"
output:
  html_document: default
---

Contact: alinat2@uci.edu

Last Updated: 6/5/2024

About: This script is the structural analysis of the Maze Learning Individual Differences (MLINDIV) project, specifically looking at young adult hippocampal subfield volumes/ thicknesses and their relationship with navigation ability.

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=F, message=F, warning=F, results=F}
# Getting started [PACKAGES AND FUNCTIONS]
# install.packages("readxl")
# install.packages("rlang")
# install.packages("ggplot2")
# install.packages("tidyr")
# install.packages("dplyr")
# install.packages("ggcorrplot")
# install.packages("stringr")
# install.packages("ppcor", repos='http://cran.us.r-project.org')
# install.packages("base64enc")
# install.packages("Hmisc")
# install.packages("readr")
# install.packages("corrplot")
# install.packages("knitr")
# install.packages("kableExtra")
devtools::install_github("kupietz/kableExtra")
# install.packages("plotrix", repos='http://cran.us.r-project.org')

library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(corrplot)
library(ggcorrplot)
library(stringr)
library(ppcor)
library(Hmisc)
library(readr)
library(corrplot)
library(knitr)
library(kableExtra)
library(plotrix)
select <- dplyr::select
```

```{r stats_functions, echo=F, message=F}
read_excel_allsheets <- function(filename, tibble = FALSE) {
  sheets <- readxl::excel_sheets(filename)
  x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
  if(!tibble) x <- lapply(x, as.data.frame)
  names(x) <- sheets
  x
}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# Calculate Bonferroni and Benjamini corrections
# nav_dv <- c("propcorrect", "patheff_acc_only", "patheff")
nav_dv <- c("propcorrect", "patheff_acc_only")

p_correction <- function(pval_table){
  # bonferroni
  pval_table$pc_bonf_p <- p.adjust(pval_table[,1], method = "bonferroni") # For the proportion correct (pc) measure
  pval_table$pe_acc_bonf_p <- p.adjust(pval_table[,2], method = "bonferroni") # For the path efficiency for correct trials only (pe_acc) measure
  # pval_table$pe_bonf_p <- p.adjust(pval_table[,3], method = "bonferroni") # For the path efficiency (pe) measure

  # BH (benjamini-hochberg)
  pval_table$pc_BH_p <- p.adjust(pval_table[,1], method = "BH")
  pval_table$pe_acc_BH_p <- p.adjust(pval_table[,2], method = "BH")
  # pval_table$pe_BH_p <- p.adjust(pval_table[,3], method = "BH")

  pval_table <- pval_table %>% select(pc_raw_p, pc_bonf_p, pc_BH_p, 
                                      pe_acc_raw_p, pe_acc_bonf_p, pe_acc_BH_p)
                                      # pe_raw_p, pe_bonf_p, pe_BH_p)
}

# p_colnames <- c("pc_raw_p", "pe_acc_raw_p", "pe_raw_p")
p_colnames <- c("pc_raw_p", "pe_acc_raw_p")
```

```{r ggplot_functions, echo=F, message=F}
# Customized plotting for knitr
ggplot_propcorr_for_knitr <- function(data, x_var, palette, title, xlab, xlim_min, xlim_max){
  ggplot(data = data, aes(y = propcorrect, x = {{x_var}})) + 
    geom_point(size = 2.5, color = palette) +
    scale_color_manual(values = palette) +
    geom_smooth(aes(color = palette), method = "lm", fill = palette) + 
    ggtitle(title) + xlab(xlab) + 
    ylab("Proportion Correct") + ylim(0, 1) + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom")
}

ggplot_patheffacc_for_knitr <- function(data, x_var, palette, title, xlab, xlim_min, xlim_max){
  ggplot(data = data, aes(y = patheff_acc_only, x = {{x_var}})) + 
    geom_point(size = 2.5, color = palette) +
    scale_color_manual(values = palette) +
    geom_smooth(aes(color = palette), method = "lm", fill = palette) + 
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (correct trials)") + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    scale_y_continuous(breaks = seq(1, 10, by = 0.05)) + ylim(1, 1.325) +
    theme(legend.position = "bottom")
}

# Customized plotting of sex diff for knitr
ggplot_propcorr_MF_for_knitr <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = propcorrect, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 2.5) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Proportion Correct") + ylim(0, 1) + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal")
}

ggplot_sbfd_propcorr_MF_for_knitr <- function(data, x_var, subfield_color, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = propcorrect, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 2.5) +
    scale_color_manual(values = c("0" = palette_sbfd[{{subfield_color}}], "1" = palette_sbfd_dark[{{subfield_color}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette_sbfd[{{subfield_color}}], "1" = palette_sbfd_dark[{{subfield_color}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Proportion Correct") + ylim(0, 1) + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal")
}

ggplot_patheff_MF_for_knitr <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 2.5) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (all trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal")
}

ggplot_patheffacc_MF_for_knitr <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff_acc_only, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 2.5) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (correct trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) + 
    scale_y_continuous(breaks = seq(1, 10, by = 0.05)) + ylim(1, 1.325) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal")
}

ggplot_sbfd_patheffacc_MF_for_knitr <- function(data, x_var, subfield_color, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff_acc_only, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 2.5) +
    scale_color_manual(values = c("0" = palette_sbfd[{{subfield_color}}], "1" = palette_sbfd_dark[{{subfield_color}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette_sbfd[{{subfield_color}}], "1" = palette_sbfd_dark[{{subfield_color}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (correct trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) + 
    scale_y_continuous(breaks = seq(1, 10, by = 0.05)) + ylim(1, 1.325) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal")
}

# Customized plotting for pdf
ggplot_propcorr_for_pdf <- function(data, x_var, palette, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = propcorrect, x = {{x_var}})) + 
    geom_point(size = 1.25, color = palette) +
    scale_color_manual(values = palette) +
    geom_smooth(aes(color = palette), method = "lm", fill = palette) + 
    ggtitle(title) + xlab(xlab) + 
    ylab("Proportion Correct") + ylim(0, 1) + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 10))
}
ggplot_patheffacc_for_pdf <- function(data, x_var, palette, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff_acc_only, x = {{x_var}})) + 
    geom_point(size = 1.25, color = palette) +
    scale_color_manual(values = palette) +
    geom_smooth(aes(color = palette), method = "lm", fill = palette) + 
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (correct trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    scale_y_continuous(breaks = seq(1, 10, by = 0.05)) + ylim(1, 1.325) +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 14),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 10))
}

# Customized plotting of sex diff for pdf
ggplot_propcorr_MF_for_pdf <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = propcorrect, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 1.25) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Proportion Correct") + ylim(0, 1) + 
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal",
          plot.title = element_text(size = 14),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 10))
}

ggplot_patheff_MF_for_pdf <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 1.25) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (all trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal",
          plot.title = element_text(size = 14),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 10))
}
ggplot_patheffacc_MF_for_pdf <- function(data, x_var, f, m, title, xlab, xlim_min, xlim_max) {
  ggplot(data = data, aes(y = patheff_acc_only, x = {{x_var}}, color = as.factor(sex))) + 
    geom_point(size = 1.25) +
    scale_color_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    scale_fill_manual(values = c("0" = palette[{{f}}], "1" = palette[{{m}}]), labels = c("F","M")) +
    labs(color = "Biological Sex") +
    geom_smooth(aes(color = as.factor(sex), fill = as.factor(sex)), method = "lm") + 
    guides(fill = "none") +
    ggtitle(title) + xlab(xlab) + 
    ylab("Excess Path Ratio (correct trials)") +
    coord_cartesian(xlim = c(xlim_min, xlim_max)) +
    scale_y_continuous(breaks = seq(1, 10, by = 0.05)) + ylim(1, 1.325) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.box = "horizontal",
          plot.title = element_text(size = 14),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text = element_text(size = 10))
}
```

```{r data, echo=F, message=F, warning=F, results=F}
# Working directory
workdir <- "/mnt/chrastil/users/alina/analysisA_FORPUBLICATION"
setwd(workdir)

# Load data
## Behavioral measures from Maze-Learning task (all participants)
data_nav_measures <- read.csv("MLINDIV_participant_full.csv") %>% 
  select("Subject", "tm_accuracy", "tm_path_efficiencies", "tm_path_efficiencies_acc_only", "n_trials") # tm = trial mean
colnames(data_nav_measures) <- c("sub_id", "propcorrect", "patheff", "patheff_acc_only", "n_completed")
data_nav_measures <- data_nav_measures[data_nav_measures["n_completed"] >= 36, ] # Removing rows w/ incomplete behavioral data

## Subject log for demographic info (all participants)
data_full <- read_excel("MLINDIV_Subject_Run_Info.xlsx")
  names(data_full)[names(data_full) == "Spatial Neuro ID"] <- "sub_id"
  names(data_full)[names(data_full) == "Sex"] <- "sex"
  names(data_full)[names(data_full) == "Age"] <- "age"
  data_full$sub_id <- extract_numeric(data_full$sub_id)
data_full <- merge(data_full[,c(1:5,7:23)], data_nav_measures[,c(1,2)], by = "sub_id", all = T) 
data_full_clean <- data_full %>% drop_na("sub_id") # Remove empty rows

## Total brain volume (all participants)
data_tiv <- read.csv(file = "TIV_comparison.csv")
  names(data_tiv)[names(data_tiv) == "SubjectNum"] <- "sub_id"
data_tiv$CaitTIV <- data_tiv$CaitTIV/1000 # Divide Caitlin's values by 1000 to match the units to others

## Volume measures and slice counts from high-res T2 HC scans
data_hrT2 <- read_excel("ASHS_volumes.xlsx", sheet = 1) 
  hres_sub_id <- c(81:83, 85, 86, 88, 89, 92:96, 98:103, 106:113)
  names(data_hrT2)[names(data_hrT2) == "Spatial Neuro ID"] <- "sub_id"
raw_vol_full <- as_tibble(read.csv("raw_vol_full.csv")) # FINAL volumes
data_hrT2[,2:15] <- raw_vol_full[,3:16] # Replace data with FINAL volumes
data_hrT2 <- merge(data_hrT2[,c(1:31,35:36)], data_nav_measures, by = "sub_id")

post_cutoff <- c(which(data_hrT2$post_cutoff == "TRUE")) # Index of subject with posterior cutoffs
data_cut <- data_hrT2[-c(post_cutoff),] # n=14, 7 subfield volumes with no posterior cutoffs

## Volume measures and slice counts from high-res T2 HC scans (body only)
data_HCbody <- read_excel("ASHS_volumes.xlsx", sheet = 2) 
  names(data_HCbody)[names(data_HCbody) == "Spatial Neuro ID"] <- "sub_id"
body_vol_full <- as_tibble(read.csv("body_vol_full.csv"))
data_HCbody[,2:13] <- body_vol_full[,3:14]
data_HCbody <- merge(data_HCbody[,c(1:29,33:34)], data_nav_measures, by = "sub_id")

post_cutoff_body <- post_cutoff[-c(5,6,9)] # Posterior cutoffs for HC body - same as full post-cutoff except 101, 102, 109
data_HCbody_cut <- data_HCbody[-c(post_cutoff_body),] # n=17, 6 subfield volumes with no posterior cutoffs

## Volume measures and slice counts from low-res T2 whole-brain scans (high-res participants only)
data_regT2 <- read_excel("ASHS_volumes.xlsx", sheet = 5)
  names(data_regT2)[names(data_regT2) == "Spatial Neuro ID"] <- "sub_id"
data_regT2 <- merge(data_regT2[,c(1:39,43:44)], data_nav_measures, by = "sub_id") 

## Volume measures and slice counts from low-res T1 whole-brain scans (all participants)
data_total_vol <- read_excel("ASHS_volumes.xlsx", sheet = 4) 
  data_total_vol$sub_id <- as.integer(data_total_vol$sub_id)
antpost_vol_full <- read.csv("antpost_vol_full.csv")
data_total_vol <- merge(data_total_vol[,c(1,4,9,11,14,19,21)], antpost_vol_full, by = "sub_id")
data_total_vol <- data_total_vol %>% 
  select("sub_id", "LHC_vol", "sLHC", "LaHC_vol", "sLaHC", "LpHC_vol", "sLpHC", 
         "RHC_vol", "sRHC", "RaHC_vol", "sRaHC", "RpHC_vol", "sRpHC", "totalHC_vol", 
         "aHC_vol", "pHC_vol", "Lpa_ratio", "Rpa_ratio", "meanpa_ratio")
data_total_vol <- merge(data_total_vol, data_nav_measures, by = "sub_id")
data_total_vol <- merge(data_total_vol, data_full_clean[,c(1,4:5)], by = "sub_id") 
data_total_vol <- merge(data_total_vol, data_tiv[,c(2,8)], by = "sub_id")
  names(data_total_vol)[names(data_total_vol) == "VaisTIV"] <- "tiv"
  
data_total_vol_ratio <- data_total_vol %>%
  mutate(aHC_vol = LaHC_vol + RaHC_vol, pHC_vol = LpHC_vol + RpHC_vol,
         Lpa_ratio = LpHC_vol/LaHC_vol, Rpa_ratio = RpHC_vol/RaHC_vol,
         meanpa_ratio = (Lpa_ratio + Rpa_ratio)/2) # pa_ratio = postHC/antHC vol ratio
  
## Pen/paper and questionnaire measures (all participants)
data_survey_scores <- read_excel_allsheets("RA_mlindiv_surveys.xlsx")
  data_survey_scores <- data_survey_scores$`Summary Scores`[,1:8]
  data_survey_scores <- merge(data_survey_scores, data_nav_measures, by = "sub_id", all = T) 
  data_survey_scores <- merge(data_survey_scores, data_full_clean[,c(1,4)], by = "sub_id", all = T) 
  data_survey_scores <- data_survey_scores %>% drop_na("propcorrect") 

# Clean data
## Define new numeric sex variable
sex_to_numeric <- function(df) {
  sex <- as.character((strsplit(gsub("[{}]","",df$`sex`), split = ",")))
  sex[sex == "M"] <- 1
  sex[sex == "F"] <- 0
  df$sex <- as.numeric(sex)
}
  
  data_hrT2$sex = sex_to_numeric(data_hrT2) #26
  data_cut$sex = sex_to_numeric(data_cut) #13
  data_HCbody$sex = sex_to_numeric(data_HCbody)
  data_total_vol$sex = sex_to_numeric(data_total_vol)
  data_total_vol_ratio$sex = sex_to_numeric(data_total_vol_ratio)
  data_regT2$sex = sex_to_numeric(data_regT2)
  data_HCbody_cut$sex = sex_to_numeric(data_HCbody_cut)
  data_survey_scores$sex = sex_to_numeric(data_survey_scores)

## Thickness
data_tdata <- data_hrT2 %>% 
  mutate(tLCA1 = LCA1/sLCA1/2, tLCA23 = LCA23/sLCA23/2, tLDG = LDG/sLDG/2, tLSUB = LSUB/sLSUB/2,
         tLERC = LERC/sLERC/2, tLPRC = LPRC/sLPRC/2, tLPHC = LPHC/sLPHC/2,
         tRCA1 = RCA1/sRCA1/2, tRCA23 = RCA23/sRCA23/2, tRDG = RDG/sRDG/2, tRSUB = RSUB/sRSUB/2,
         tRERC = RERC/sRERC/2, tRPRC = RPRC/sRPRC/2, tRPHC = RPHC/sRPHC/2) %>% # 2mm
  dplyr::select("sub_id","tLCA1","tLCA23","tLDG","tLSUB","tLERC","tLPRC","tLPHC","tRCA1","tRCA23","tRDG","tRSUB",
                "tRERC","tRPRC","tRPHC","sex","age","propcorrect","patheff","patheff_acc_only","tiv") 
  # n=26, 7 HC subfield

data_tHCbody_cut <- data_HCbody_cut %>% 
  mutate(tLCA1 = LCA1/sLCA1/2, tLCA23 = LCA23/sLCA23/2, tLDG = LDG/sLDG/2, tLSUB = LSUB/sLSUB/2, 
         tLPRC = LPRC/sLPRC/2, tLPHC = LPHC/sLPHC/2,
         tRCA1 = RCA1/sRCA1/2, tRCA23 = RCA23/sRCA23/2, tRDG = RDG/sRDG/2, tRSUB = RSUB/sRSUB/2,
         tRPRC = RPRC/sRPRC/2, tRPHC = RPHC/sRPHC/2) %>% # 2mm
  dplyr::select("sub_id","tLCA1","tLCA23","tLDG","tLSUB","tLPRC","tLPHC","tRCA1","tRCA23","tRDG","tRSUB",
                "tRPRC","tRPHC","sex","age","propcorrect","patheff","patheff_acc_only","tiv") # n=17, 6 body subfields

data_tregT2 <- data_regT2 %>%
  mutate(tLaHC = LaHC/sLaHC/0.94, tLpHC = LpHC/sLpHC/0.94, 
         tLERC = LERC/sLERC/0.94, tLPRC = LPRC/sLPRC/0.94, tLPHC = LPHC/sLPHC/0.94, 
         tRaHC = RaHC/sRaHC/0.94, tRpHC = RpHC/sRpHC/0.94, 
         tRERC = RERC/sRERC/0.94, tRPRC = RPRC/sRPRC/0.94, tRPHC = RPHC/sRPHC/0.94) %>% # 0.94mm
  dplyr::select("sub_id","tLaHC","tLpHC","tLERC","tLPRC","tLPHC","tRaHC","tRpHC","tRERC","tRPRC","tRPHC",
                "sex","age","propcorrect","patheff","patheff_acc_only","tiv") # n=26, 5 HC/MTL subfields

data_total_thick <- data_total_vol %>% 
  mutate(tLHC = LHC_vol/sLHC/0.94, tLaHC = LaHC_vol/sLaHC/0.94, tLpHC = LpHC_vol/sLpHC/0.94,
         tRHC = RHC_vol/sRHC/0.94, tRaHC = RaHC_vol/sRaHC/0.94, tRpHC = RpHC_vol/sRpHC/0.94) %>% # 0.94mm
  dplyr::select("sub_id","tLHC","tLaHC","tLpHC","tRHC","tRaHC","tRpHC",
                "sex","age","propcorrect","patheff","patheff_acc_only","tiv") # n=99, L/R ant/post/total

# Define relevant variables
subfields_LR <- c("LCA1", "RCA1", "LCA23", "RCA23", "LDG", "RDG", "LSUB", "RSUB",
                  "LERC", "RERC", "LPRC", "RPRC", "LPHC", "RPHC")

# Compare TIV values between UCI and UCSB (Vaisakh, Vini, Caitlin) -> no signif difference, will use Vaisakh's values
t.test(data_tiv$VaisTIV, data_tiv$ViniTIV)
t.test(data_tiv$VaisTIV, data_tiv$CaitTIV)
```

```{r ladder, echo=F, message=F, warning=F, results=F, fig.show='hide'}
# Ladder plot for performance (EXPLORATORY)
ladder_data_26 <- data_regT2 %>% select(propcorrect, patheff_acc_only) %>% 
  mutate(propcorrect = (propcorrect - mean(propcorrect))/sd(propcorrect),
         patheff_acc_only = (patheff_acc_only - mean(patheff_acc_only))/sd(patheff_acc_only)) %>%
  mutate(patheff_acc_only = patheff_acc_only*(-1))

ladderplot(ladder_data_26, scale = TRUE, col = 1, pch = 19, lty = 1, vertical = TRUE, ordered = FALSE)

ladder_data_26_all <- data_regT2 %>% select(propcorrect, patheff) %>% 
  mutate(propcorrect = (propcorrect - mean(propcorrect))/sd(propcorrect),
         patheff = (patheff - mean(patheff))/sd(patheff)) %>%
  mutate(patheff = patheff*(-1))

ladderplot(ladder_data_26_all, scale = TRUE, col = 1, pch = 19, lty = 1, vertical = TRUE, ordered = FALSE)

ladder_data_99 <- data_total_vol %>% select(propcorrect, patheff_acc_only) %>% 
  mutate(propcorrect = (propcorrect - mean(propcorrect))/sd(propcorrect),
         patheff_acc_only = (patheff_acc_only - mean(patheff_acc_only))/sd(patheff_acc_only)) %>%
  mutate(patheff_acc_only = patheff_acc_only*(-1))

ladderplot(ladder_data_99, scale = TRUE, col = 1, pch = 19, lty = 1, vertical = TRUE, ordered = FALSE)

ladder_data_99_all <- data_total_vol %>% select(propcorrect, patheff) %>% 
  mutate(propcorrect = (propcorrect - mean(propcorrect))/sd(propcorrect),
         patheff = (patheff - mean(patheff))/sd(patheff)) %>%
  mutate(patheff = patheff*(-1))

ladderplot(ladder_data_99_all, scale = TRUE, col = 1, pch = 19, lty = 1, vertical = TRUE, ordered = FALSE)
```

```{r ggplot, echo=F, message=F, warning=F}
# Color palettes + graph themes
library(tidyr)
# Colorblind-friendly palette (https://venngage.com/blog/color-blind-friendly-palette/)
# palette <- c("#f2d39f", "#fca405", "#cc6424", "#84b7f3", "#2c548c", "#898989", "#595959") # tan, light/dark orange, light/dark blue, light/dark gray
# palette <- c("#92c0d7", "#6fabd0", "#295982", "#b0d5c7", "#8accb3", "#477977", "#b99976", "#664229", "#b57ec9", "#683578")
palette <- c("#92c0d7", "#6fabd0", "#295982", "#b0d5c7", "#8accb3", "#477977", "#b99976", "#2c548c", "#b57ec9", "#683578")
palette_sbfd <- c("#bd0000", "#49a12f", "#1306cf", "#4e819c", "#c9991e", "#921c94", "#438f8e", "#8e7ba8", "#74917b")
                  # CA1, CA2/3, DG, SUB, ERC, PRC, PHC, aHC, pHC
palette_sbfd_dark <- c("#5e0000", "#245017", "#090367", "#27404e", "#644c0f", "#490e4a", "#214747", "#473d54", "#3a483d")

# New theme
baseTheme <- theme_get() # store the default theme
theme_set(theme_minimal()) 
theme_update1 <- theme_update(text = element_text(colour = rgb(12, 35, 75, maxColorValue = 255)), 
                              axis.title = element_text(size = 20, color = "black"),
                              axis.text = element_text(size = 16, color = "black"),
                              axis.line.x = element_blank(),
                              axis.line.y = element_blank(),
                              legend.position = c(0.8, 0.8),
                              legend.background = element_rect(fill = "white", size = 0.2, linetype = "solid"),
                              legend.box.background = element_rect(color = "black"),
                              legend.direction = "horizontal",
                              legend.box = "vertical",
                              legend.title = element_text(size = 9, color = "black"),
                              legend.text = element_text(size = 8, color = "black"),
                              plot.title = element_text(size = 20, hjust = 0.5, color = "black"),
                              strip.text = element_text(size = 10, color = "black"),
                              panel.grid.major = element_blank(),
                              panel.grid.minor = element_blank(),
                              panel.border = element_rect(color = "black", fill="transparent", size=0.5),
                              plot.background = element_rect(fill = "transparent", color = "transparent"))
theme1 <- theme_get()
```

```{r summary-data, echo=F, results=F}
## Summary
dim(data_total_vol)
print(nrow(data_total_vol) - sum(data_total_vol$sex)) # number of females
mean(data_total_vol$age)
sd(data_total_vol$age)
summary(data_total_vol$age)

dim(data_hrT2)
print(nrow(data_hrT2) - sum(data_hrT2$sex)) # number of females
mean(data_hrT2$age)
sd(data_hrT2$age)
summary(data_hrT2$age)

cor.test(data_total_vol$propcorrect, data_total_vol$patheff_acc_only)
```

```{r ggplot_behav, echo=F, message=F, results=F, warning=F}
# Correlation plot for performance
ggplot_propcorr_for_knitr(data_total_vol, patheff_acc_only, "gray40", 
                          "Correlation of Navigation Measures", "Excess Path Ratio (correct trials)", 1, 1.325)
# pdf.options()
pdf("figures/Figure_1-4.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_for_pdf(data_total_vol, patheff_acc_only, "gray40", 
                              "Correlation of Navigation Measures", "Excess Path Ratio (correct trials)", 1, 1.325))

invisible(dev.off())
```

## Total Volumes + Propcorrect or Patheff (n=99)

```{r total_vol-outlier, echo=F, results=F}
# Testing null hypotheses
# Check for outliers
which(abs(scale(data_total_vol$LHC_vol)) > 3)
which(abs(scale(data_total_vol$RHC_vol)) > 3)
which(abs(scale(data_total_vol$totalHC_vol)) > 3)

dim(data_total_vol)
```

```{r total_vol-corr, echo=F}
## Function that outputs correlation table for all 3 regions
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 3 subfields' r and p-values
subfields_total <- c("LHC_vol", "RHC_vol", "totalHC_vol")
corr_mat_total <- function(stats_list) {
  corr_mat_total <- matrix(unlist(t(stats_list)), byrow=T, 3, 2)
  colnames(corr_mat_total) <- c("r", "p-value")
  rownames(corr_mat_total) <- c("LHC", "RHC", "totalHC")
  return(corr_mat_total)
}

pval_table <- data.frame(row.names = c("LHC","RHC"))

# Partial correlation tables between L/R/total HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_vol[subfd_name]), data_total_vol[dv], 
                                  c(data_total_vol$sex, data_total_vol$age, data_total_vol$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table <- cbind(pval_table, stats[c(2,4),])
}
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
colnames(pval_table) <- p_colnames
p_corrected <- p_correction(pval_table)
p_corrected
```

### propcorrect

```{r total_vol-ggplot, echo=F, message=F, fig.keep='none', out.width='50%'}
ggplot_propcorr_for_knitr(data_total_vol, LHC_vol, palette[7], "Left Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_propcorr_for_knitr(data_total_vol, RHC_vol, palette[7], "Right Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_propcorr_for_knitr(data_total_vol, totalHC_vol, palette[7], "Total Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r total_vol-sex, echo=F, results='hide'}
# Correlation stratified by sex
data_total_vol_F <- data_total_vol[(data_total_vol['sex'] == 0), ]
nrow(data_total_vol_F)
data_total_vol_M <- data_total_vol[(data_total_vol['sex'] == 1), ]
nrow(data_total_vol_M)
```

#### Females (n=46)

```{r total_vol-female, echo=F}
pval_table_f <- data.frame(row.names = c("LHC_f","RHC_f"))

# Female: partial correlation tables between L/R/total HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=46)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_vol_F[subfd_name]), data_total_vol_F[dv], 
                                  c(data_total_vol_F$age, data_total_vol_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table_f <- cbind(pval_table_f, stats[c(2,4),])
}

colnames(pval_table_f) <- p_colnames
```

#### Males (n=53)

```{r total_vol-male, echo=F}
pval_table_m <- data.frame(row.names = c("LHC_m", "RHC_m"))

# Male: partial correlation tables between L/R/total HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=53)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_vol_M[subfd_name]), data_total_vol_M[dv], 
                                  c(data_total_vol_M$age, data_total_vol_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table_m <- cbind(pval_table_m, stats[c(2,4),])
}

colnames(pval_table_m) <- p_colnames
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
p_corrected_f <- p_correction(pval_table_f)
p_corrected_m <- p_correction(pval_table_m)

p_corrected <- rbind(p_corrected_f, p_corrected_m)
p_corrected
```

### propcorrect

```{r total_vol-ggplot_propcorr_MF, echo=F, fig.show='hold', message=FALSE, out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_vol, LHC_vol, 7, 8, "Left Hippocampus", bquote("Volume"~(mm^3)), 3100, 5550)
ggplot_propcorr_MF_for_knitr(data_total_vol, RHC_vol, 7, 8, "Right Hippocampus", bquote("Volume"~(mm^3)), 3100, 5550)
ggplot_propcorr_MF_for_knitr(data_total_vol, totalHC_vol, 7, 8, "Total Hippocampus", bquote("Volume"~(mm^3)), 6500, 10750)
```

```{r total_vol-ggplot_propcorr_MF_for_pdf-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_5-1.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, LHC_vol, 7, 8, "Left Hippocampus", bquote("Volume"~(mm^3)), 3100, 5550) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_5-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, RHC_vol, 7, 8, "Right Hippocampus", bquote("Volume"~(mm^3)), 3100, 5550) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_5-3.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, totalHC_vol, 7, 8, "Total Hippocampus", bquote("Volume"~(mm^3)), 6500, 10750) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r total_vol-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep="none"}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_vol, LHC_vol, 7, 8, "Left Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, RHC_vol, 7, 8, "Right Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, totalHC_vol, 7, 8, "Total Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r total_vol-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ LHC_vol, data = data_total_vol) # Replace the X value with diff HC subdivisions
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_vol$LHC_vol, data_total_vol$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)
  
## Pearson's correlation tables between L/R/total HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
    
  for (subfd_name in subfields_total) { 
    corr_test <- cor.test(pull(data_total_vol[subfd_name]), data_total_vol[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
    
  print(dv)
  print(corr_mat_total(stats))
}

## Multiple linear regression
model_LHC_propcorr <- lm(propcorrect ~ LHC_vol + sex + age + tiv, data = data_total_vol)
# model_LHC_patheff <- lm(patheff ~ LHC_vol + sex + age + tiv, data = data_total_vol)
model_LHC_patheffacc <- lm(patheff_acc_only ~ LHC_vol + sex + age + tiv, data = data_total_vol)
model_RHC_propcorr <- lm(propcorrect ~ RHC_vol + sex + age + tiv, data = data_total_vol)
# model_RHC_patheff <- lm(patheff ~ RHC_vol + sex + age + tiv, data = data_total_vol)
model_RHC_patheffacc <- lm(patheff_acc_only ~ RHC_vol + sex + age + tiv, data = data_total_vol)
model_totalHC_propcorr <- lm(propcorrect ~ totalHC_vol + sex + age + tiv, data = data_total_vol)
# model_totalHC_patheff <- lm(patheff ~ totalHC_vol + sex + age + tiv, data = data_total_vol)
model_totalHC_patheffacc <- lm(patheff_acc_only ~ totalHC_vol + sex + age + tiv, data = data_total_vol)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_vol$age, data_total_vol$propcorrect)
  # # No multicollinearity
  # vif(model_LHC_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_LHC_propcorr) # Replace the value with diff models
  # plot(fitted(model_LHC_propcorr), resid) 
  # # Multivariate normality
  
summary(model_LHC_propcorr)
summary(model_RHC_propcorr) # *the only ones Weisberg et al. 2019 looked at*
summary(model_totalHC_propcorr)

# summary(model_LHC_patheff)
# summary(model_RHC_patheff) # *the only ones Weisberg et al. 2019 looked at*
# summary(model_totalHC_patheff)

summary(model_LHC_patheffacc)
summary(model_RHC_patheffacc) # *the only ones Weisberg et al. 2019 looked at*
summary(model_totalHC_patheffacc)
  
  model_LaHC <- lm(propcorrect ~ LaHC_vol + sex + age + tiv, data = data_total_vol)
  model_LpHC <- lm(propcorrect ~ LpHC_vol + sex + age + tiv, data = data_total_vol)
  model_RaHC <- lm(propcorrect ~ RaHC_vol + sex + age + tiv, data = data_total_vol)
  model_RpHC <- lm(propcorrect ~ RpHC_vol + sex + age + tiv, data = data_total_vol)
  summary(model_LaHC)
  summary(model_LpHC)
  summary(model_RaHC)
  summary(model_RpHC) # *the only one Weisberg et al. 2019 looked at*
```

## Total Thickness + Propcorr or Patheff (n=98)

```{r total_thick-outlier, echo=F, results=F}
# Testing null hypotheses
# Check for outliers
which(abs(scale(data_total_thick$tLHC)) > 3)
which(abs(scale(data_total_thick$tRHC)) > 3) # 20

dim(data_total_thick)

# Remove outliers
data_total_thick_rm <- data_total_thick[-c(20),] # Participant 24
dim(data_total_thick_rm)
```

```{r total_thick-corr, echo=F}
## Function that outputs correlation table for all 2 regions
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 2 subfields' r and p-values
subfields_total <- c("tLHC", "tRHC")
corr_mat_total <- function(stats_list) {
  corr_mat_total <- matrix(unlist(t(stats_list)), byrow=T, 2, 2)
  colnames(corr_mat_total) <- c("r", "p-value")
  rownames(corr_mat_total) <- c("tLHC", "tRHC")
  return(corr_mat_total)
}

pval_table <- data.frame(row.names = c("LHC","RHC"))

# Outliers removed: Partial correlation tables between L/R HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=98)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm[subfd_name]), data_total_thick_rm[dv], 
                                  c(data_total_thick_rm$sex, data_total_thick_rm$age, data_total_thick_rm$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table <- cbind(pval_table, stats[c(2,4),])
}

# ggplot(data = data_total_thick_rm, aes(y = propcorrect, x = tLHC)) + 
#   geom_point(color = palette[6]) + geom_smooth(method = "lm", color = palette[6]) +
#   ggtitle("Wayfinding Success and Left HC Thickness") + xlab("Normalized Thickness Ratio") +
#   ylab("Proportion Correct") + ylim(0, 1)
# ggplot(data = data_total_thick_rm, aes(y = propcorrect, x = tRHC)) + 
#   geom_point(color = palette[6]) + geom_smooth(method = "lm", color = palette[6]) +
#   ggtitle("Wayfinding Success and Right HC Thickness") + xlab("Normalized Thickness Ratio") +
#   ylab("Proportion Correct") + ylim(0, 1)
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
colnames(pval_table) <- p_colnames
p_corrected <- p_correction(pval_table)
p_corrected
```

```{r total_thick-sex, echo=F, results='hide'}
# Correlation stratified by sex
data_total_thick_rm_F <- data_total_thick_rm[(data_total_thick_rm['sex'] == 0), ]
nrow(data_total_thick_rm_F)
data_total_thick_rm_M <- data_total_thick_rm[(data_total_thick_rm['sex'] == 1), ]
nrow(data_total_thick_rm_M)
```

#### Females (n=46)

```{r total_thick-female, echo=F}
pval_table_f <- data.frame(row.names = c("LHC_f","RHC_f"))

# Female: partial correlation tables between L/R/total HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=46)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm_F[subfd_name]), data_total_thick_rm_F[dv], 
                                  c(data_total_thick_rm_F$age, data_total_thick_rm_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table_f <- cbind(pval_table_f, stats[c(2,4),])
}

colnames(pval_table_f) <- p_colnames
```

#### Males (n=52)

```{r total_thick-male, echo=F}
pval_table_m <- data.frame(row.names = c("LHC_m", "RHC_m"))

# Male: partial correlation tables between L/R/total HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=52)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm_M[subfd_name]), data_total_thick_rm_M[dv], 
                                  c(data_total_thick_rm_M$age, data_total_thick_rm_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
  pval_table_m <- cbind(pval_table_m, stats[c(2,4),])
}

colnames(pval_table_m) <- p_colnames
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
p_corrected_f <- p_correction(pval_table_f)
p_corrected_m <- p_correction(pval_table_m)

p_corrected <- rbind(p_corrected_f, p_corrected_m)
p_corrected
```

### propcorrect

```{r total_thick-ggplot_propcorr_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_thick_rm, tRHC, 7, 8, "Right Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
```

```{r total_thick-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep="none"}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tLHC, 7, 8, "Left Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tRHC, 7, 8, "Right Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
```

```{r total_thick-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ tLHC, data = data_total_thick_rm) # Replace the X and Y with diff value
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_thick_rm$tLHC, data_total_thick_rm$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)

## Outliers removed: Pearson's correlation tables between L/R HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=98)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_total) { 
    corr_test <- cor.test(pull(data_total_thick_rm[subfd_name]), data_total_thick_rm[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_total(stats))
}

## Multiple linear regression
model_tLHC_propcorr <- lm(propcorrect ~ tLHC + sex + age + tiv, data = data_total_thick_rm)
# model_tLHC_patheff <- lm(patheff ~ tLHC + sex + age + tiv, data = data_total_thick_rm)
model_tLHC_patheffacc <- lm(patheff_acc_only ~ tLHC + sex + age + tiv, data = data_total_thick_rm)
model_tRHC_propcorr <- lm(propcorrect ~ tRHC + sex + age + tiv, data = data_total_thick_rm)
# model_tRHC_patheff <- lm(patheff ~ tRHC + sex + age + tiv, data = data_total_thick_rm)
model_tRHC_patheffacc <- lm(patheff_acc_only ~ tRHC + sex + age + tiv, data = data_total_thick_rm)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_thick_rm$age, data_total_thick_rm$propcorrect)
  # # No multicollinearity
  # vif(model_tLHC_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_tLHC_propcorr) # Replace the value with diff models
  # plot(fitted(model_tLHC_propcorr), resid) 
  # # Multivariate normality

summary(model_tLHC_propcorr)
summary(model_tRHC_propcorr) # *the only ones Weisberg et al. 2019 looked at*

#summary(model_tLHC_patheff)
#summary(model_tRHC_patheff) # *the only ones Weisberg et al. 2019 looked at*

summary(model_tLHC_patheffacc)
summary(model_tRHC_patheffacc) # *the only ones Weisberg et al. 2019 looked at*
```

## Bilateral Ant/Post Volumes + Propcorr or Patheff (n=99)

```{r bi_apvol-outlier, echo=F, results=F}
# Check for outliers
which(abs(scale(data_total_vol$LaHC_vol)) > 3)
which(abs(scale(data_total_vol$LpHC_vol)) > 3)
which(abs(scale(data_total_vol$RaHC_vol)) > 3)
which(abs(scale(data_total_vol$RpHC_vol)) > 3)

dim(data_total_vol)
```

```{r bi_apvol-corr, echo=F}
## Function that outputs correlation table for all 4 subregions
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 4 subregions' r and p-values
subfields_antpost <- c("LaHC_vol", "LpHC_vol", "RaHC_vol", "RpHC_vol")
corr_mat_antpost <- function(stats_list) {
  corr_mat_antpost <- matrix(unlist(t(stats_list)), byrow=T, 4, 2)
  colnames(corr_mat_antpost) <- c("r", "p-value")
  rownames(corr_mat_antpost) <- c("LaHC", "LpHC", "RaHC", "RpHC")
  return(corr_mat_antpost)
}

p <- data.frame(row.names = c("LaHC", "LpHC", "RaHC", "RpHC"))

# Partial correlation tables between L/R ant/post volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol[subfd_name]), data_total_vol[dv], 
                                  c(data_total_vol$sex, data_total_vol$age, data_total_vol$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
  pval_table <- cbind(pval_table, stats[c(2,4),])
}
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
colnames(pval_table) <- p_colnames
p_corrected <- p_correction(pval_table)
p_corrected
```

### propcorrect

```{r bi_apvol-ggplot, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_for_knitr(data_total_vol, LaHC_vol, palette_sbfd[8], "Left Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_propcorr_for_knitr(data_total_vol, RaHC_vol, palette_sbfd[8], "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r bi_apvol-sex, echo=F, results=F}
# Correlation stratified by sex
data_total_vol_F <- data_total_vol[(data_total_vol['sex'] == 0), ]
nrow(data_total_vol_F)
data_total_vol_M <- data_total_vol[(data_total_vol['sex'] == 1), ]
nrow(data_total_vol_M)
```

#### Females (n=46)

```{r bi_apvol-female, echo=F}
pval_table_f <- data.frame(row.names = c("LaHC_f", "LpHC_f", "RaHC_f", "RpHC_f"))

# Female: partial correlation tables between L/R ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=46)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol_F[subfd_name]), data_total_vol_F[dv], 
                                  c(data_total_vol_F$age, data_total_vol_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
  pval_table_f <- cbind(pval_table_f, stats[c(2,4),])
}

colnames(pval_table_f) <- p_colnames
```

#### Males (n=53)

```{r bi_apvol-male, echo=F}
pval_table_m <- data.frame(row.names = c("LaHC_m", "LpHC_m", "RaHC_m", "RpHC_m"))

# Male: partial correlation tables between L/R ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=53)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol_M[subfd_name]), data_total_vol_M[dv], 
                                  c(data_total_vol_M$age, data_total_vol_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
  pval_table_m <- cbind(pval_table_m, stats[c(2,4),])
}

colnames(pval_table_m) <- p_colnames
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
p_corrected_f <- p_correction(pval_table_f)
p_corrected_m <- p_correction(pval_table_m)

p_corrected <- rbind(p_corrected_f, p_corrected_m)
p_corrected
```

### propcorrect

```{r bi_apvol-ggplot_propcorr_MF_for_pdf, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_vol, LaHC_vol, 2, 3, "Left Anterior Hippocampus", bquote("Volume"~(mm^3)), 990, 3100)
ggplot_propcorr_MF_for_knitr(data_total_vol, LpHC_vol, 5, 6, "Left Posterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 2825)
ggplot_propcorr_MF_for_knitr(data_total_vol, RaHC_vol, 2, 3, "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), 990, 3100)
ggplot_propcorr_MF_for_knitr(data_total_vol, RpHC_vol, 5, 6, "Right Posterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 2825)
```

```{r bi_apvol-ggplot_propcorr_MF_for_pdf-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_7-1.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, LaHC_vol, 2, 3, "Left Anterior Hippocampus", bquote("Volume"~(mm^3)), 990, 3100) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, LpHC_vol, 5, 6, "Left Posterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 2825) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-3.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, RaHC_vol, 2, 3, "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), 990, 3100) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-4.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, RpHC_vol, 5, 6, "Right Posterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 2825) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r bi_apvol-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep='none'}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_vol, LaHC_vol, 2, 3, "Left Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, LpHC_vol, 5, 6, "Left Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, RaHC_vol, 2, 3, "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, RpHC_vol, 5, 6, "Right Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

### patheff (correct trials)

```{r bi_apvol-ggplot_patheffacc_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_patheffacc_MF_for_knitr(data_total_vol, LaHC_vol, 2, 3, "Left Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_patheffacc_MF_for_knitr(data_total_vol, LpHC_vol, 5, 6, "Left Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_patheffacc_MF_for_knitr(data_total_vol, RaHC_vol, 2, 3, "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 3100)
ggplot_patheffacc_MF_for_knitr(data_total_vol, RpHC_vol, 5, 6, "Right Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r bi_apvol-ggplot_patheffacc_MF-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_8-1.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_patheffacc_MF_for_pdf(data_total_vol, RaHC_vol, 2, 3, "Right Anterior Hippocampus", bquote("Volume"~(mm^3)), 1300, 3100) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r bi_apvol-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ LHC_vol, data = data_total_vol) # Replace the X value with diff HC subdivisions
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_vol$LaHC_vol, data_total_vol$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)

## Pearson's correlation tables between L/R ant/post volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    corr_test <- cor.test(pull(data_total_vol[subfd_name]), data_total_vol[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}

## Multiple linear regression
model_LaHC_propcorr <- lm(propcorrect ~ LaHC_vol + sex + age + tiv, data = data_total_vol)
# model_LaHC_patheff <- lm(patheff ~ LaHC_vol + sex + age + tiv, data = data_total_vol)
model_LaHC_patheffacc <- lm(patheff_acc_only ~ LaHC_vol + sex + age + tiv, data = data_total_vol)
model_LpHC_propcorr <- lm(propcorrect ~ LpHC_vol + sex + age + tiv, data = data_total_vol)
# model_LpHC_patheff <- lm(patheff ~ LpHC_vol + sex + age + tiv, data = data_total_vol)
model_LpHC_patheffacc <- lm(patheff_acc_only ~ LpHC_vol + sex + age + tiv, data = data_total_vol)
model_RaHC_propcorr <- lm(propcorrect ~ RaHC_vol + sex + age + tiv, data = data_total_vol)
# model_RaHC_patheff <- lm(patheff ~ RaHC_vol + sex + age + tiv, data = data_total_vol)
model_RaHC_patheffacc <- lm(patheff_acc_only ~ RaHC_vol + sex + age + tiv, data = data_total_vol)
model_RpHC_propcorr <- lm(propcorrect ~ RpHC_vol + sex + age + tiv, data = data_total_vol)
# model_RpHC_patheff <- lm(patheff ~ RpHC_vol + sex + age + tiv, data = data_total_vol)
model_RpHC_patheffacc <- lm(patheff_acc_only ~ RpHC_vol + sex + age + tiv, data = data_total_vol)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_vol$age, data_total_vol$propcorrect)
  # # No multicollinearity
  # vif(model_LaHC_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_LaHC_propcorr) # Replace the value with diff models
  # plot(fitted(model_LaHC_propcorr), resid) 
  # # Multivariate normality

summary(model_LaHC_propcorr)
# summary(model_LaHC_patheff)
summary(model_LaHC_patheffacc)
summary(model_LpHC_propcorr)
# summary(model_LpHC_patheff)
summary(model_LpHC_patheffacc)
summary(model_RaHC_propcorr)
# summary(model_RaHC_patheff) 
summary(model_RaHC_patheffacc) 
summary(model_RpHC_propcorr) # *the only ones steve looked at*
# summary(model_RpHC_patheff) # *the only ones steve looked at*
summary(model_RpHC_patheffacc) # *the only ones steve looked at*
```

## Bilateral Ant/Post Thickness + Propcorr or Patheff (n=98)

```{r bi_apthick-outlier, echo=F, results=F}
# Check for outliers
which(abs(scale(data_total_thick$tLaHC)) > 3) # 20
which(abs(scale(data_total_thick$tLpHC)) > 3) 
which(abs(scale(data_total_thick$tRaHC)) > 3) # 20
which(abs(scale(data_total_thick$tRpHC)) > 3)

# Remove outliers
data_total_thick_rm <- data_total_thick[-c(20),]
dim(data_total_thick_rm)
```

```{r bi_apthick-corr, echo=F}
## Function that outputs correlation table for all 4 subregions
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 4 subregions' r and p-values
subfields_antpost <- c("tLaHC", "tLpHC", "tRaHC", "tRpHC")
corr_mat_antpost <- function(stats_list) {
  corr_mat_antpost <- matrix(unlist(t(stats_list)), byrow=T, 4, 2)
  colnames(corr_mat_antpost) <- c("r", "p-value")
  rownames(corr_mat_antpost) <- subfields_antpost
  return(corr_mat_antpost)
}

# Partial correlation tables between L/R ant/post thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=98)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm[subfd_name]), data_total_thick_rm[dv], 
                                  c(data_total_thick_rm$sex, data_total_thick_rm$age, data_total_thick_rm$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}
```

### propcorrect

```{r bi_apthick-ggplot, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_for_knitr(data_total_thick_rm, tLaHC, palette_sbfd[8], "Left Anterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
```

```{r bi_apthick-sex, echo=F, results=F}
# Correlation stratified by sex
data_total_thick_rm_F <- data_total_thick_rm[(data_total_thick_rm['sex'] == 0), ]
nrow(data_total_thick_rm_F)
data_total_thick_rm_M <- data_total_thick_rm[(data_total_thick_rm['sex'] == 1), ]
nrow(data_total_thick_rm_M)
```

#### Females (n=46)

```{r bi_apthick-female, echo=F}
pval_table_f <- data.frame(row.names = c("LaHC_f", "LpHC_f", "RaHC_f", "RpHC_f"))

# Female: partial correlation tables between L/R ant/post HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=46)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm_F[subfd_name]), data_total_thick_rm_F[dv], 
                                  c(data_total_thick_rm_F$age, data_total_thick_rm_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
  pval_table_f <- cbind(pval_table_f, stats[c(2,4),])
}

colnames(pval_table_f) <- p_colnames
```

#### Males (n=52)

```{r bi_apthick-male, echo=F}
pval_table_m <- data.frame(row.names = c("LaHC_m", "LpHC_m", "RaHC_m", "RpHC_m"))
  
# Male: partial correlation tables between L/R ant/post HC thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=52)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_thick_rm_M[subfd_name]), data_total_thick_rm_M[dv], 
                                  c(data_total_thick_rm_M$age, data_total_thick_rm_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
  pval_table_m <- cbind(pval_table_m, stats[c(2,4),])
}

colnames(pval_table_m) <- p_colnames
```

### raw pval, bonferroni pval, BH pval

```{r echo=F}
p_corrected_f <- p_correction(pval_table_f)
p_corrected_m <- p_correction(pval_table_m)

p_corrected <- rbind(p_corrected_f, p_corrected_m)
p_corrected
```

### propcorrect

```{r bi_apthick-ggplot_propcorr_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_thick_rm, tLaHC, 2, 3, "Left Anterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
ggplot_propcorr_MF_for_knitr(data_total_thick_rm, tLpHC, 5, 6, "Left Posterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
ggplot_propcorr_MF_for_knitr(data_total_thick_rm, tRaHC, 2, 3, "Right Anterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
ggplot_propcorr_MF_for_knitr(data_total_thick_rm, tRpHC, 5, 6, "Right Posterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
```

```{r bi_apthick-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep='none'}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tLaHC, 2, 3, "Left Anterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tLpHC, 5, 6, "Left Posterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tRaHC, 2, 3, "Right Anterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_thick_rm, tRpHC, 5, 6, "Right Posterior Hippocampus", "Normalized Thickness Ratio", NULL, NULL)
```

```{r bi_apthick-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ tLpHC, data = data_total_thick_rm) # Replace the X value with diff HC subdivisions
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_thick_rm$tLaHC, data_total_thick_rm$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)

## Pearson's correlation tables between L/R ant/post thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    corr_test <- cor.test(pull(data_total_thick_rm[subfd_name]), data_total_thick_rm[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}

## Multiple linear regression
model_tLaHC_propcorr <- lm(propcorrect ~ tLaHC + sex + age + tiv, data = data_total_thick_rm)
# model_tLaHC_patheff <- lm(patheff ~ tLaHC + sex + age + tiv, data = data_total_thick_rm)
model_tLaHC_patheffacc <- lm(patheff_acc_only ~ tLaHC + sex + age + tiv, data = data_total_thick_rm)
model_tLpHC_propcorr <- lm(propcorrect ~ tLpHC + sex + age + tiv, data = data_total_thick_rm)
# model_tLpHC_patheff <- lm(patheff ~ tLpHC + sex + age + tiv, data = data_total_thick_rm)
model_tLpHC_patheffacc <- lm(patheff_acc_only ~ tLpHC + sex + age + tiv, data = data_total_thick_rm)
model_tRaHC_propcorr <- lm(propcorrect ~ tRaHC + sex + age + tiv, data = data_total_thick_rm)
# model_tRaHC_patheff <- lm(patheff ~ tRaHC + sex + age + tiv, data = data_total_thick_rm)
model_tRaHC_patheffacc <- lm(patheff_acc_only ~ tRaHC + sex + age + tiv, data = data_total_thick_rm)
model_tRpHC_propcorr <- lm(propcorrect ~ tRpHC + sex + age + tiv, data = data_total_thick_rm)
# model_tRpHC_patheff <- lm(patheff ~ tRpHC + sex + age + tiv, data = data_total_thick_rm)
model_tRpHC_patheffacc <- lm(patheff_acc_only ~ tRpHC + sex + age + tiv, data = data_total_thick_rm)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_thick_rm$age, data_total_thick_rm$propcorrect)
  # # No multicollinearity
  # vif(model_tLaHC_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_tLaHC_propcorr) # Replace the value with diff models
  # plot(fitted(model_tLaHC_propcorr), resid)
  # # Multivariate normality

summary(model_tLaHC_propcorr)
# summary(model_tLaHC_patheff)
summary(model_tLaHC_patheffacc)
summary(model_tLpHC_propcorr)
# summary(model_tLpHC_patheff)
summary(model_tLpHC_patheffacc)
summary(model_tRaHC_propcorr)
# summary(model_tRaHC_patheff) 
summary(model_tRaHC_patheffacc) 
summary(model_tRpHC_propcorr) 
# summary(model_tRpHC_patheff) 
summary(model_tRpHC_patheffacc) 
```

## Total Ant/Post Volumes + Propcorr or Patheff (n=99)

```{r total_apvol-outlier, echo=F, results=F}
# Check for outliers
which(abs(scale(data_total_vol$aHC_vol)) > 3)
which(abs(scale(data_total_vol$pHC_vol)) > 3)
```

```{r total_apvol-corr, echo=F}
## Function that outputs correlation table for 2 subregions
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 2 subregions' r and p-values
subfields_antpost <- c("aHC_vol", "pHC_vol")
corr_mat_antpost <- function(stats_list) {
  corr_mat_antpost <- matrix(unlist(t(stats_list)), byrow=T, 2, 2)
  colnames(corr_mat_antpost) <- c("r", "p-value")
  rownames(corr_mat_antpost) <- c("aHC", "pHC")
  return(corr_mat_antpost)
}

# Partial correlation tables between total ant/post volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol[subfd_name]), data_total_vol[dv], 
                                  c(data_total_vol$sex, data_total_vol$age, data_total_vol$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}
```

### propcorrect

```{r total_apvol-ggplot, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_for_knitr(data_total_vol, aHC_vol, palette_sbfd[8], "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r total_apvol-sex, echo=F, results=F}
# Correlation stratified by sex
data_total_vol_F <- data_total_vol[(data_total_vol['sex'] == 0), ]
nrow(data_total_vol_F)
data_total_vol_M <- data_total_vol[(data_total_vol['sex'] == 1), ]
nrow(data_total_vol_M)
```

#### Females (n=46)

```{r total_apvol-female, echo=F}
# Female: partial correlation tables between total ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=46)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol_F[subfd_name]), data_total_vol_F[dv], 
                                  c(data_total_vol_F$age, data_total_vol_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}
```

#### Males (n=53)

```{r total_apvol-male, echo=F}
# Male: partial correlation tables between total ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=53)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    partial_corr <- pcor.test(pull(data_total_vol_M[subfd_name]), data_total_vol_M[dv], 
                                  c(data_total_vol_M$age, data_total_vol_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}
```

### propcorrect

```{r total_apvol-ggplot_propcorr_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_vol, aHC_vol, 2, 3, "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), 2250, 5900)
ggplot_propcorr_MF_for_knitr(data_total_vol, pHC_vol, 5, 6, "Total Posterior Hippocampus", bquote("Volume"~(mm^3)), 2700, 5200)
```

```{r total_apvol-ggplot_propcorr_MF-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_7-5.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, aHC_vol, 2, 3, "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), 2250, 5900) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-6.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, pHC_vol, 5, 6, "Total Posterior Hippocampus", bquote("Volume"~(mm^3)), 2700, 5200) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r total_apvol-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep='none'}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_vol, aHC_vol, 2, 3, "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
# ggplot_patheff_MF_for_knitr(data_total_vol, pHC_vol, 5, 6, "Total Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

### patheff (correct trials)

```{r total_apvol-ggplot_patheffacc_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_patheffacc_MF_for_knitr(data_total_vol, aHC_vol, 2, 3, "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), 2500, 5950)
ggplot_patheffacc_MF_for_knitr(data_total_vol, pHC_vol, 5, 6, "Total Posterior Hippocampus", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r total_apvol-ggplot_patheffacc_MF-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_8-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(ggplot_patheffacc_MF_for_pdf(data_total_vol, aHC_vol, 2, 3, "Total Anterior Hippocampus", bquote("Volume"~(mm^3)), 2500, 5950) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r total_apvol-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ aHC_vol, data = data_total_vol) # Replace the X value with diff HC subdivisions
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_vol$pHC_vol, data_total_vol$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)

## Pearson's correlation tables between total ant/post volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=99)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_antpost) { 
    corr_test <- cor.test(pull(data_total_vol[subfd_name]), data_total_vol[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_antpost(stats))
}

## Multiple linear regression
model_aHC_propcorr <- lm(propcorrect ~ aHC_vol + sex + age + tiv, data = data_total_vol)
# model_aHC_patheff <- lm(patheff ~ aHC_vol + sex + age + tiv, data = data_total_vol)
model_aHC_patheffacc <- lm(patheff_acc_only ~ aHC_vol + sex + age + tiv, data = data_total_vol)
model_pHC_propcorr <- lm(propcorrect ~ pHC_vol + sex + age + tiv, data = data_total_vol)
# model_pHC_patheff <- lm(patheff ~ pHC_vol + sex + age + tiv, data = data_total_vol)
model_pHC_patheffacc <- lm(patheff_acc_only ~ pHC_vol + sex + age + tiv, data = data_total_vol)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_vol$aHC_vol, data_total_vol$propcorrect)
  # # No multicollinearity
  # vif(model_aHC_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_aHC_propcorr) # Replace the value with diff models
  # plot(fitted(model_aHC_propcorr), resid) 
  # # Multivariate normality

summary(model_aHC_propcorr)
# summary(model_aHC_patheff)
summary(model_aHC_patheffacc)
summary(model_pHC_propcorr)
# summary(model_pHC_patheff)
summary(model_pHC_patheffacc)
```

## L/R/Mean Post/Ant Ratio + Propcorr or Patheff (n=96)

```{r paratio-outlier, echo=F, results=F}
# Check for outliers
which(abs(scale(data_total_vol_ratio$Lpa_ratio)) > 3) # 66
which(abs(scale(data_total_vol_ratio$Rpa_ratio)) > 3) # 21, 26
which(abs(scale(data_total_vol_ratio$meanpa_ratio)) > 3) # 21

# Remove outliers
data_total_vol_ratio_rm <- data_total_vol_ratio[-c(21, 26, 66),] # Participants 25, 31, 76
```

```{r paratio-corr, echo=F}
## Function that outputs correlation table for 3 measures
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 3 measures' r and p-values
subfields_ratio <- c("Lpa_ratio", "Rpa_ratio", "meanpa_ratio")
corr_mat_ratio <- function(stats_list) {
  corr_mat_ratio <- matrix(unlist(t(stats_list)), byrow=T, 3, 2)
  colnames(corr_mat_ratio) <- c("r", "p-value")
  rownames(corr_mat_ratio) <- subfields_ratio
  return(corr_mat_ratio)
}

# Outliers removed: Partial correlation between L/R post/ant HC vol ratio and propcorrect, patheff_acc_only (and, optionally, patheff) (n=96)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_ratio) { 
    partial_corr <- pcor.test(pull(data_total_vol_ratio_rm[subfd_name]), data_total_vol_ratio_rm[dv], 
                                  c(data_total_vol_ratio_rm$sex, data_total_vol_ratio_rm$age, data_total_vol_ratio_rm$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_ratio(stats))
}
```

### propcorrect

```{r paratio-ggplot, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_for_knitr(data_total_vol_ratio_rm, Lpa_ratio, palette[7], "Left pHC/aHC Ratio", "Left PostHC/AntHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_propcorr_for_knitr(data_total_vol_ratio_rm, Rpa_ratio, palette[7], "Right pHC/aHC Ratio", "Right PostHC/AntHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_propcorr_for_knitr(data_total_vol_ratio_rm, meanpa_ratio, palette[7], "Mean pHC/aHC Ratio", "Mean PostHC/AntHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
```

```{r paratio-sex, echo=F, results=F}
# Correlation stratified by sex
data_total_vol_ratio_rm_F <- data_total_vol_ratio_rm[(data_total_vol_ratio_rm['sex'] == 0), ]
nrow(data_total_vol_ratio_rm_F)
data_total_vol_ratio_rm_M <- data_total_vol_ratio_rm[(data_total_vol_ratio_rm['sex'] == 1), ]
nrow(data_total_vol_ratio_rm_M)
```

#### Females (n=44)

```{r paratio-female, echo=F}
# Female: partial correlation tables between total ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=44)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_ratio) { 
    partial_corr <- pcor.test(pull(data_total_vol_F[subfd_name]), data_total_vol_F[dv], 
                                  c(data_total_vol_F$age, data_total_vol_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_ratio(stats))
}
```

#### Males (n=52)

```{r paratio-male, echo=F}
# Male: partial correlation tables between total ant/post HC volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=52)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_ratio) { 
    partial_corr <- pcor.test(pull(data_total_vol_M[subfd_name]), data_total_vol_M[dv], 
                                  c(data_total_vol_M$age, data_total_vol_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_ratio(stats))
}
```

### propcorrect

```{r paratio-ggplot_propcorr_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_propcorr_MF_for_knitr(data_total_vol, Lpa_ratio, 9, 10, "Left pHC/aHC Ratio", "Left postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_propcorr_MF_for_knitr(data_total_vol, Rpa_ratio, 9, 10, "Right pHC/aHC Ratio", "Right postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_propcorr_MF_for_knitr(data_total_vol, meanpa_ratio, 9, 10, "Mean pHC/aHC Ratio", "Mean postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
```

```{r paratio-ggplot_propcorr_MF-pdf, echo=F, message=F, results=F}
pdf("figures/Figure_7-7.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.8)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, Lpa_ratio, 9, 10, "Left pHC/aHC Ratio", "Left postHC/antHC Ratio", 0.275, 1.725) +
        geom_vline(xintercept = 1, linetype = 2, color = palette[7]) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-8.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.8)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, Rpa_ratio, 9, 10, "Right pHC/aHC Ratio", "Right postHC/antHC Ratio", 0.275, 1.725) +
        geom_vline(xintercept = 1, linetype = 2, color = palette[7]) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())

pdf("figures/Figure_7-9.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.8)

print(ggplot_propcorr_MF_for_pdf(data_total_vol, meanpa_ratio, 9, 10, "Mean pHC/aHC Ratio", "Mean postHC/antHC Ratio", 0.275, 1.725) +
        geom_vline(xintercept = 1, linetype = 2, color = palette[7]) +
        geom_smooth(color = "gray40", method = "lm", se = FALSE, linetype = "dashed"))

invisible(dev.off())
```

```{r paratio-ggplot_patheff_MF_for_pdf, echo=F, message=F, results=F, fig.keep='none'}
### patheff (all trials)
# ggplot_patheff_MF_for_knitr(data_total_vol, Lpa_ratio, 9, 10, "Left pHC/aHC Ratio", "Left postHC/antHC Ratio", 0.275, 1.725) +
#   geom_vline(xintercept = 1, linetype = 2, color = palette[7])
# ggplot_patheff_MF_for_knitr(data_total_vol, Rpa_ratio, 9, 10, "Right pHC/aHC Ratio", "Right postHC/antHC Ratio", 0.275, 1.725) +
#   geom_vline(xintercept = 1, linetype = 2, color = palette[7])
# ggplot_patheff_MF_for_knitr(data_total_vol, meanpa_ratio, 9, 10, "Mean pHC/aHC Ratio", "Mean postHC/antHC Ratio", 0.275, 1.725) +
#   geom_vline(xintercept = 1, linetype = 2, color = palette[7])
```

### patheff (correct trials)

```{r paratio-ggplot_patheffacc_MF, echo=F, message=F, fig.show='hold', out.width='50%'}
ggplot_patheffacc_MF_for_knitr(data_total_vol, Lpa_ratio, 9, 10, "Left pHC/aHC Ratio", "Left postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_patheffacc_MF_for_knitr(data_total_vol, Rpa_ratio, 9, 10, "Right pHC/aHC Ratio", "Right postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
ggplot_patheffacc_MF_for_knitr(data_total_vol, meanpa_ratio, 9, 10, "Mean pHC/aHC Ratio", "Mean postHC/antHC Ratio", 0.275, 1.725) +
  geom_vline(xintercept = 1, linetype = 2, color = palette[7])
```

```{r paratio-mlr, echo=F, results=F}
# MULTIPLE LINEAR REGRESSION - CANNOT DO PARTIAL CORRECTION WITH SEX?
## Pearson correlation: Assumptions check
  # # Homoscedasticity = constant variance
  # model <- lm(propcorrect ~ Lpa_ratio, data = data_total_vol_ratio_rm) # Replace the X value with diff HC subdivisions
  # resid <- resid(model)
  # plot(fitted(model), resid)
  # # Linearity
  # plot(data_total_vol_ratio_rm$Lpa_ratio, data_total_vol_ratio_rm$propcorrect) # Replace the X value with diff HC subdivisions
  # # Good to use pearson's correlation :)

## Pearson's correlation tables between total ant/post volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=96)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_ratio) { 
    corr_test <- cor.test(pull(data_total_vol_ratio_rm[subfd_name]), data_total_vol_ratio_rm[,dv], method = "pearson")
    stats <- rbind(stats, round(corr_test$estimate, digits = 3), round(corr_test$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(corr_test$estimate, digits = 2), 
    #             "and p-value is:", round(corr_test$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_ratio(stats))
}

## Multiple linear regression
model_Lratio_propcorr <- lm(propcorrect ~ Lpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
# model_Lratio_patheff <- lm(patheff ~ Lpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
model_Lratio_patheffacc <- lm(patheff_acc_only ~ Lpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
model_Rratio_propcorr <- lm(propcorrect ~ Rpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
# model_Rratio_patheff <- lm(patheff ~ Rpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
model_Rratio_patheffacc <- lm(patheff_acc_only ~ Rpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
model_meanratio_propcorr <- lm(propcorrect ~ meanpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
# model_meanratio_patheff <- lm(patheff ~ meanpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)
model_meanratio_patheffacc <- lm(patheff_acc_only ~ meanpa_ratio + sex + age + tiv, data = data_total_vol_ratio_rm)

  # # Assumptions check:
  # # Linearity
  # plot(data_total_vol_ratio_rm$Lpa_ratio, data_total_vol_ratio_rm$propcorrect)
  # # No multicollinearity
  # vif(model_Lratio_propcorr) # Replace the value with diff models. outcome values should be less than 5
  # # Independent observations
  # # Homoscedasticity = constant variance
  # resid <- resid(model_Lratio_propcorrect) # Replace the value with diff models
  # plot(fitted(model_Lratio_propcorrect), resid) 
  # # Multivariate normality

summary(model_Lratio_propcorr)
# summary(model_Lratio_patheff)
summary(model_Lratio_patheffacc)
summary(model_Rratio_propcorr)
# summary(model_Rratio_patheff)
summary(model_Rratio_patheffacc)
summary(model_meanratio_propcorr)
# summary(model_meanratio_patheff)
summary(model_meanratio_patheffacc)
```

## *No cut-off* HR-T2 Subfield Volumes + Propcorr or Patheff (n=14)

```{r 14vol, echo=F, results=F}
## Function that outputs correlation table for all 7 subfields
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 7 subfields' r and p-values
subfields_all <- c("CA1", "CA2/3", "DG", "SUB", "ERC", "PRC", "PHC")
corr_mat_allsub <- function(stats_list) {
  corr_mat_allsub <- matrix(unlist(t(stats_list)), byrow=T, 7, 4)
  colnames(corr_mat_allsub) <- c("(Left) r", "p-value", "(Right) r", "p-value")
  rownames(corr_mat_allsub) <- subfields_all
  return(corr_mat_allsub)
}

output_adjusted_pvals <- function(stats_list, subfields_list){
  pcorr_results <- as.data.frame(matrix(unlist(stats_list), nrow = length(subfields_list), ncol = 4, byrow = TRUE))
  colnames(pcorr_results) <- c("(Left) r", "(Left) p", "(Right) r", "(Right) p")
  rownames(pcorr_results) <- subfields_list
  
  p_bonfadj <- p.adjust(c(pcorr_results$`(Left) p`, pcorr_results$`(Right) p`), method = "bonferroni")
  p_BHadj <- p.adjust(c(pcorr_results$`(Left) p`, pcorr_results$`(Right) p`), method = "BH")

  p_adjusted <- matrix(cbind(sprintf("%.4f", round(p_bonfadj, digits = 4)), sprintf("%.4f", round(p_BHadj, digits = 4))), 
                       nrow = length(subfields_list), ncol = 4, byrow = FALSE)
  pcorr_results <- cbind(pcorr_results, p_adjusted)
  colnames(pcorr_results) <- c("(Left) r", "(Left) p", "(Right) r", "(Right) p", 
                               "(Left) p_bonf", "(Right) p_bonf", "(Left) p_BH", "(Right) p_BH")
  pcorr_results <- pcorr_results %>% select("(Left) r", "(Left) p", "(Left) p_bonf", "(Left) p_BH",
                                            "(Right) r", "(Right) p", "(Right) p_bonf", "(Right) p_BH",)
}

dim(data_cut)
```

```{r 14vol_corrmatrix, echo=F, warning=F, results=F, fig.show='hold'}
detailed_matrix <- cor.mtest(data.frame(data_cut[2:15]))
correlation_matrix <- cor(data_cut[2:15])

# corrplot(correlation_matrix, method = "color", type = "lower", tl.col = "black", diag = FALSE,
#          title = "Correlation of Subfield Volumes n=14",
#          addCoef.col = 'black', 
#          p.mat = detailed_matrix$p, sig.level = 0.05)

# corrplot(correlation_matrix, p.mat = detailed_matrix$p, method = 'color', type = 'lower',
#          tl.col = "black", tl.cex = 0.7,
#          insig = 'label_sig', pch.cex = 0.5, pch.col = "white",
#          addCoef.col ='black', number.cex = 0.5, diag=FALSE,
#          cl.cex = 0.5)

# To see significant correlations
# corrplot.mixed(correlation_matrix, lower = "color", upper = "number", 
#                p.mat = detailed_matrix$p, insig = 'label_sig',
#                number.cex = 0.65, tl.cex = 0.55, tl.col = "black", cl.cex = 0.55)

corrplot.mixed(correlation_matrix, lower = "color", upper = "number", 
               number.cex = 0.65, tl.cex = 0.55, tl.col = "black", cl.cex = 0.55)

# pdf.options()
pdf("figures/Figure_2-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 4)

print(corrplot.mixed(correlation_matrix, lower = "color", upper = "number", 
               number.cex = 0.5, tl.cex = 0.4, tl.col = "black", cl.cex = 0.4))

invisible(dev.off())
```

```{r 14vol-corr, echo=F, warning=F, results='asis'}
# Partial correlation tables between no cutoff subfield volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=14)
for (dv in nav_dv) {
  stats <- NULL;

  for (subfd_name in subfields_LR) { 
    partial_corr <- pcor.test(pull(data_cut[subfd_name]), data_cut[dv], 
                              c(data_cut$sex, data_cut$age, data_cut$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }

  # print(corr_mat_allsub(stats))  
  pcorr_results <- output_adjusted_pvals(stats, subfields_all)
  
  variable_name <- paste0(dv, "_results")
  assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
}

print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

### propcorrect

```{r 14vol-ggplot_propcorr-knitr, echo=F, message=F, fig.show='hold', out.width='50%', fig.align='center'}
ggplot_propcorr_for_knitr(data_cut, LCA1, palette_sbfd[1], 
                            "Left CA1", bquote("Volume"~(mm^3)), NULL, NULL)

ggplot_propcorr_for_knitr(data_cut, LCA23, palette_sbfd[2], 
                            "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r 14vol-ggplot_propcorr-pdf, echo=F, message=F, results=F, warning=F}
pdf("figures/Figure_3-1.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.35)

print(ggplot_propcorr_for_pdf(data_cut, LCA1, palette_sbfd[1], "Left CA1", bquote("Volume"~(mm^3)), NULL, NULL))

invisible(dev.off())

pdf("figures/Figure_3-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.35)

print(ggplot_propcorr_for_pdf(data_cut, LCA23, palette_sbfd[2], "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL))

invisible(dev.off())
```

### patheff (correct trials)

```{r 14vol-ggplot, echo=F, message=F, fig.show='hold', out.width='50%', fig.align='center'}
ggplot_patheffacc_for_knitr(data_cut, LCA23, palette_sbfd[2], "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r 14vol-ggplot_patheffacc-pdf, echo=F, message=F, results=F, warning=F}
pdf("figures/Figure_4-1.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.35)

print(ggplot_patheffacc_for_pdf(data_cut, LCA23, palette_sbfd[2], "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL))

invisible(dev.off())
```

### Females and Males

```{r 14vol-sex, echo=F, results=F}
# Correlation stratified by sex
data_cut_F <- data_cut[(data_cut['sex'] == 0), ]
nrow(data_cut_F)
data_cut_M <- data_cut[(data_cut['sex'] == 1), ]
nrow(data_cut_M)
```

#### Females (n=6)

```{r 14vol-female, echo=F}
# Female: partial correlation tables between HC subfield volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=6)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_LR) { 
    partial_corr <- pcor.test(pull(data_cut_F[subfd_name]), data_cut_F[dv], 
                                  c(data_cut_F$age, data_cut_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_allsub(stats))
}
```

#### Males (n=8)

```{r 14vol-male, echo=F}
# Male: partial correlation tables between HC subfield volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=8)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_LR) { 
    partial_corr <- pcor.test(pull(data_cut_M[subfd_name]), data_cut_M[dv], 
                                  c(data_cut_M$age, data_cut_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_allsub(stats))
}
```

```{r 14vol-ggplot_propcorr_MF-knitr, echo=F, message=F, fig.show='hold', out.width='25%'}
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LCA1, 1, "Left CA1", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RCA1, 1, "Right CA1", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LCA23, 2, "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RCA23, 2, "Right CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LDG, 3, "Left DG", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RDG, 3, "Right DG", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LSUB, 4, "Left SUB", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RSUB, 4, "Right SUB", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LERC, 5, "Left ERC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RERC, 5, "Right ERC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LPRC, 6, "Left PRC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RPRC, 6, "Right PRC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, LPHC, 7, "Left PHC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_cut, RPHC, 7, "Right PHC", bquote("Volume"~(mm^3)), NULL, NULL)
```

```{r 14vol-ggplot_patheffacc_MF-knitr, echo=F, message=F, fig.show='hold', out.width='25%'}
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LCA1, 1, "Left CA1", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RCA1, 1, "Right CA1", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LCA23, 2, "Left CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RCA23, 2, "Right CA2/3", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LDG, 3, "Left DG", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RDG, 3, "Right DG", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LSUB, 4, "Left SUB", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RSUB, 4, "Right SUB", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LERC, 5, "Left ERC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RERC, 5, "Right ERC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LPRC, 6, "Left PRC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RPRC, 6, "Right PRC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, LPHC, 7, "Left PHC", bquote("Volume"~(mm^3)), NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_cut, RPHC, 7, "Right PHC", bquote("Volume"~(mm^3)), NULL, NULL)
```

## *No cut-off* HR-T2 Subfield Thickness + Propcorr or Patheff (n=26)

```{r 26thick, echo=F, results=F}
# Subfield thickness
subfields_tHC_LR <- NULL;

for (subfd_name in subfields_LR) {
  subfields_tHC_LR <- rbind(subfields_tHC_LR, paste("t", subfd_name, sep = ""))
}
subfields_tHC_LR <- subfields_tHC_LR[,1]

dim(data_tdata)
```

```{r 26thick-corr, echo=F, results='asis'}
# Partial correlation tables between subfield thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=26)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_tHC_LR) { 
    partial_corr <- pcor.test(pull(data_tdata[subfd_name]), data_tdata[dv], 
                                   c(data_tdata$sex, data_tdata$age, data_tdata$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  # print(corr_mat_allsub(stats))  
  pcorr_results <- output_adjusted_pvals(stats, subfields_all)
  
  variable_name <- paste0(dv, "_results")
  assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
}

print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

```{r 26thick-ggplot_propcorr-knitr, echo=F, message=F, fig.show='hold', out.width='50%', fig.align='center'}
ggplot_propcorr_for_knitr(data_tdata, tLDG, palette_sbfd[3], 
                             "Left DG", "Normalized Thickness Ratio", NULL, NULL)
```

```{r 26thick-ggplot_propcorr-pdf, echo=F, message=F, results=F, warning=F}
pdf("figures/Figure_3-3.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.25)

print(ggplot_propcorr_for_pdf(data_tdata, tLDG, palette_sbfd[3], "Left DG Thickness", "Normalized Thickness Ratio", NULL, NULL))

invisible(dev.off())
```

### Females and Males

```{r 26thick-sex, echo=F, results=F}
# Correlation stratified by sex
data_tdata_F <- data_tdata[(data_tdata['sex'] == 0), ]
nrow(data_tdata_F)
data_tdata_M <- data_tdata[(data_tdata['sex'] == 1), ]
nrow(data_tdata_M)
```

#### Females (n=13)

```{r 26thick-female, echo=F}
# Female: partial correlation tables between HC subfield thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=13)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_tHC_LR) { 
    partial_corr <- pcor.test(pull(data_tdata_F[subfd_name]), data_tdata_F[dv], 
                                  c(data_tdata_F$age, data_tdata_F$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_allsub(stats))
}
```

#### Males (n=13)

```{r 26thick-male, echo=F}
# Male: partial correlation tables between HC subfield thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=13)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_tHC_LR) { 
    partial_corr <- pcor.test(pull(data_tdata_M[subfd_name]), data_tdata_M[dv], 
                                  c(data_tdata_M$age, data_tdata_M$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 3), round(partial_corr$p.value, digits = 5))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  print(dv)
  print(corr_mat_allsub(stats))
}
```

### propcorrect (n=26, thickness)

```{r 26thick-ggplot_propcorr_MF-knitr, echo=F, message=F, fig.show='hold', out.width='25%'}
ggplot_propcorr_for_knitr(data_tdata, tLCA1, palette_sbfd[1], "Left CA1", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLCA1, 1, "Left CA1", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRCA1, palette_sbfd[1], "Right CA1", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRCA1, 1, "Right CA1", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLCA23, palette_sbfd[2], "Left CA2/3", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLCA23, 2, "Left CA2/3", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRCA23, palette_sbfd[2], "Right CA2/3", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRCA23, 2, "Right CA2/3", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLDG, palette_sbfd[3], "Left DG", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLDG, 3, "Left DG", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRDG, palette_sbfd[3], "Right DG", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRDG, 3, "Right DG", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLSUB, palette_sbfd[4], "Left SUB", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLSUB, 4, "Left SUB", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRSUB, palette_sbfd[4], "Right SUB", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRSUB, 4, "Right SUB", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLERC, palette_sbfd[5], "Left ERC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLERC, 5, "Left ERC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRERC, palette_sbfd[5], "Right ERC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRERC, 5, "Right ERC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLPRC, palette_sbfd[6], "Left PRC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLPRC, 6, "Left PRC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRPRC, palette_sbfd[6], "Right PRC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRPRC, 6, "Right PRC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tLPHC, palette_sbfd[7], "Left PHC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tLPHC, 7, "Left PHC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_propcorr_for_knitr(data_tdata, tRPHC, palette_sbfd[7], "Right PHC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_propcorr_MF_for_knitr(data_tdata, tRPHC, 7, "Right PHC", "Normalized Thickness Ratio", NULL, NULL)
```

### path eff for correct trials (n=26, thickness)

```{r 26thick-ggplot_patheffacc_MF-knitr, echo=F, message=F, fig.show='hold', out.width='25%'}
ggplot_patheffacc_for_knitr(data_tdata, tLCA1, palette_sbfd[1], "Left CA1", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLCA1, 1, "Left CA1", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRCA1, palette_sbfd[1], "Right CA1", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRCA1, 1, "Right CA1", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLCA23, palette_sbfd[2], "Left CA2/3", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLCA23, 2, "Left CA2/3", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRCA23, palette_sbfd[2], "Right CA2/3", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRCA23, 2, "Right CA2/3", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLDG, palette_sbfd[3], "Left DG", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLDG, 3, "Left DG", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRDG, palette_sbfd[3], "Right DG", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRDG, 3, "Right DG", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLSUB, palette_sbfd[4], "Left SUB", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLSUB, 4, "Left SUB", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRSUB, palette_sbfd[4], "Right SUB", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRSUB, 4, "Right SUB", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLERC, palette_sbfd[5], "Left ERC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLERC, 5, "Left ERC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRERC, palette_sbfd[5], "Right ERC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRERC, 5, "Right ERC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLPRC, palette_sbfd[6], "Left PRC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLPRC, 6, "Left PRC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRPRC, palette_sbfd[6], "Right PRC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRPRC, 6, "Right PRC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tLPHC, palette_sbfd[7], "Left PHC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tLPHC, 7, "Left PHC", "Normalized Thickness Ratio", NULL, NULL)

ggplot_patheffacc_for_knitr(data_tdata, tRPHC, palette_sbfd[7], "Right PHC", "Normalized Thickness Ratio", NULL, NULL)
ggplot_sbfd_patheffacc_MF_for_knitr(data_tdata, tRPHC, 7, "Right PHC", "Normalized Thickness Ratio", NULL, NULL)
```

## HR-T2 *Body-only* Subfield Volumes + Propcorr or Patheff (n=17)
[Not analyzed in manuscript]

```{r 17vol, echo=F, results=F}
# ## Function that outputs correlation table for 6 subfields
# ## Inputs: (1) list of correlation (r) values and p-values
# ## Output: a correlation matrix (mat)/ table for the 6 subfields' r and p-values
# subfields_4 <- c("CA1", "CA2/3", "DG", "SUB")
# corr_mat_4sub <- function(stats_list) {
#   corr_mat_4sub <- matrix(unlist(t(stats_list)), byrow=T, 4, 4)
#   colnames(corr_mat_4sub) <- c("(Left) r", "p-value", "(Right) r", "p-value")
#   rownames(corr_mat_4sub) <- subfields_4
#   return(corr_mat_4sub)
# }
# 
# subfields_LR4 <- subfields_LR[-c(9:14)]
# 
# dim(data_HCbody_cut)
```

```{r 17vol-corr, echo=F, warning=F, results='asis'}
# # Partial correlation tables between body-only subfield volumes and propcorrect, patheff_acc_only  (and, optionally, patheff) (n=17)
# for (dv in nav_dv) {
#   stats <- NULL;
#   
#   for (subfd_name in subfields_LR4) { 
#     partial_corr <- pcor.test(pull(data_HCbody_cut[subfd_name]), data_HCbody_cut[dv], 
#                                   c(data_HCbody_cut$sex, data_HCbody_cut$age, data_HCbody_cut$tiv), method = "pearson")
#     stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
#     # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
#     #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
#   }
#   
#   # print(corr_mat_4sub(stats))
# 
#   pcorr_results <- output_adjusted_pvals(stats, subfields_4)
#   
#   variable_name <- paste0(dv, "_results")
#   assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
# }
# 
# print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# # print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

```{r 17vol-ggplot, echo=F, message=F, fig.show='hold', out.width='50%', fig.align='center'}
### patheff (correct trials)

# ggplot_patheffacc_for_knitr(data_HCbody_cut, RCA1, palette_sbfd[1], "Right CA1 Body", bquote("Volume"~(mm^3)), NULL, NULL)
```

## HR-T2 *Body-only* Subfield Thickness + Propcorr or Patheff (n=17)
[Not analyzed in manuscript]

```{r 17thick-corr, echo=F, warning=F, results='asis'}
# subfields_tLR4 <- subfields_tHC_LR[-c(9:14)]
# 
# # Partial correlation tables between body-only subfield thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=17)
# for (dv in nav_dv) {
#   stats <- NULL;
#   
#   for (subfd_name in subfields_tLR4) { 
#     partial_corr <- pcor.test(pull(data_tHCbody_cut[subfd_name]), data_tHCbody_cut[dv], 
#                                   c(data_tHCbody_cut$sex, data_tHCbody_cut$age, data_tHCbody_cut$tiv), method = "pearson")
#     stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
#     # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
#     #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
#   }
#   
#   # print(corr_mat_4sub(stats))
# 
#   pcorr_results <- output_adjusted_pvals(stats, subfields_4)
#   
#   variable_name <- paste0(dv, "_results")
#   assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
# }
# 
# print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# # print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

```{r 17thick-ggplot, echo=F, message=F, fig.show='hold', out.width='50%', fig.align='center'}
### patheff (correct trials)

# ggplot_patheffacc_for_knitr(data_tHCbody_cut, tLCA1, palette_sbfd[1], 
#                              "Left CA1 Body", "Normalized Thickness Ratio", NULL, NULL)
```

## Full Reg-T2 Subfield Volumes + Propcorr or Patheff (n=26)

```{r 26vol, echo=F, results=F}
## Function that outputs correlation table for all 5 subfields
## Inputs: (1) list of correlation (r) values and p-values
## Output: a correlation matrix (mat)/ table for the 5 subfields' r and p-values
subfields_regT2 <- c("aHC", "pHC", "ERC", "PRC", "PHC")
subfields_LRregT2 <- c("LaHC", "RaHC", "LpHC", "RpHC", "LERC", "RERC", "LPRC", "RPRC", "LPHC", "RPHC")
corr_mat_5sub <- function(stats_list) {
  corr_mat_5sub <- matrix(unlist(t(stats_list)), byrow=T, 5, 4)
  colnames(corr_mat_5sub) <- c("(Left) r", "p-value", "(Right) r", "p-value")
  rownames(corr_mat_5sub) <- subfields_regT2
  return(corr_mat_5sub)
}

dim(data_regT2)
```

```{r 26vol-corr, echo=F, warning=F, results='asis'}
# Partial correlation tables between manual regT2 subfield volumes and propcorrect, patheff_acc_only (and, optionally, patheff) (n=26)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_LRregT2) { 
    partial_corr <- pcor.test(pull(data_regT2[subfd_name]), data_regT2[dv], 
                                  c(data_regT2$sex, data_regT2$age, data_regT2$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  # print(corr_mat_5sub(stats))  
  
  pcorr_results <- output_adjusted_pvals(stats, subfields_regT2)
  
  variable_name <- paste0(dv, "_results")
  assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
}

print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

### patheff (correct trials)

```{r 26vol-ggplot, echo=F, message=F, warning=F, fig.show='hold', out.width='50%'}
ggplot_patheffacc_for_knitr(data_regT2, RERC, palette_sbfd[5], "Right Entorhinal Cortex", bquote("Volume"~(mm^3)), 775, 2000)
ggplot_patheffacc_for_knitr(data_regT2, LPHC, palette_sbfd[7], "Left Parahippocampal Cortex", bquote("Volume"~(mm^3)), 1500, 3025)
```

```{r 26vol-ggplot_patheffacc-pdf, echo=F, message=F, results=F, warning=F}
pdf("figures/Figure_4-2.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.35)

ggplot_patheffacc_for_pdf(data_regT2, RERC, palette_sbfd[5], "Right Entorhinal Cortex", bquote("Volume"~(mm^3)), 775, 2000)

invisible(dev.off())

pdf("figures/Figure_4-3.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.35)

ggplot_patheffacc_for_pdf(data_regT2, LPHC, palette_sbfd[7], "Left Parahippocampal Cortex", bquote("Volume"~(mm^3)), 1500, 3025)

invisible(dev.off())
```

## Full Reg-T2 Subfield Thickness + Propcorr or Patheff (n=26)

```{r 26thick-corr2, echo=F, warning=F, results='asis'}
# Create function: correlation table for 5 subfields
subfields_regT2 <- c("aHC", "pHC", "ERC", "PRC", "PHC")
corr_mat_5sub <- function(stats_list) {
  corr_mat_5sub <- matrix(unlist(t(stats_list)), byrow=T, 5, 4)
  colnames(corr_mat_5sub) <- c("(Left) r", "p-value", "(Right) r", "p-value")
  rownames(corr_mat_5sub) <- subfields_regT2
  return(corr_mat_5sub)
}

subfields_tLRregT2 <- NULL;
for (subfd_name in subfields_LRregT2) {
  subfields_tLRregT2 <- rbind(subfields_tLRregT2, paste("t", subfd_name, sep = ""))
}
subfields_tLRregT2 <- subfields_tLRregT2[,1]

# Partial correlation tables between manual regT2 subfield thickness and propcorrect, patheff_acc_only (and, optionally, patheff) (n=26)
for (dv in nav_dv) {
  stats <- NULL;
  
  for (subfd_name in subfields_tLRregT2) { 
    partial_corr <- pcor.test(pull(data_tregT2[subfd_name]), data_tregT2[dv], 
                                   c(data_tregT2$sex, data_tregT2$age, data_tregT2$tiv), method = "pearson")
    stats <- rbind(stats, round(partial_corr$estimate, digits = 2), round(partial_corr$p.value, digits = 4))
    # print(paste(i, "estimate is:", round(partial_corr$estimate, digits = 2), 
    #             "and p-value is:", round(partial_corr$p.value, digits = 3))) 
  }
  
  # print(corr_mat_5sub(stats))  
  
  pcorr_results <- output_adjusted_pvals(stats, subfields_regT2)
  
  variable_name <- paste0(dv, "_results")
  assign(variable_name, pcorr_results) # propcorrect_results, patheff_results, patheff_acc_only_results
}

print(kable_styling(kable(propcorrect_results, caption = "propcorrect"), full_width = FALSE, position = "center"))
# print(kable_styling(kable(patheff_results, caption = "patheff (all trials)"), full_width = FALSE, position = "center"))
print(kable_styling(kable(patheff_acc_only_results, caption = "patheff (correct trials)"), full_width = FALSE, position = "center"))
```

### patheff (correct trials)

```{r 26thick-ggplot, echo=F, message=F, warning=F, fig.show='hold', out.width='50%', fig.align='center'}
ggplot_patheffacc_for_knitr(data_tregT2, tRERC, palette_sbfd[5], "Right Entorhinal Cortex", "Normalized Thickness Ratio", NULL, NULL)
```

```{r 26thick-ggplot_patheffacc-pdf, echo=F, message=F, results=F, warning=F}
pdf("figures/Figure_4-4.pdf", onefile = TRUE, family = "sans", bg = "transparent",
    width = 4, height = 3.25)

ggplot_patheffacc_for_pdf(data_tregT2, tRERC, palette_sbfd[5], "Right Entorhinal Cortex", "Normalized Thickness Ratio", NULL, NULL)

invisible(dev.off())
```
